---
output: cynkratemplate::readme_document
---

<!-- README.md and index.md are generated from README.Rmd.
     Edit that file and render it the usual way: rmarkdown::render(),
     devtools::build_readme(), or the Knit button. The cynkratemplate
     package must be installed; it supplies the output format. -->

```{r setup, include = FALSE}
# Keep the render reproducible: `Rprof()` samples on a wall-clock timer, so
# how many samples it collects depends on how fast and how loaded the
# machine is. Normalise the count, as other READMEs here normalise memory
# addresses.
knitr::knit_hooks$set(document = function(x, options) {
  gsub("Profile data: [0-9]+ samples", "Profile data: <n> samples", x)
})
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)

pkgload::load_all()
```
# profile

<!-- badges: start -->
[![rcc](https://github.com/r-prof/profile/workflows/rcc/badge.svg)](https://github.com/r-prof/profile/actions)
[![Codecov test coverage](https://codecov.io/gh/r-prof/profile/graph/badge.svg)](https://app.codecov.io/gh/r-prof/profile/tree/main)
[![CRAN status](https://www.r-pkg.org/badges/version/profile)](https://cran.r-project.org/package=profile)
<!-- badges: end -->

The goal of profile is to read and write files that contain run time profiling data. Currently, *profile* supports:

- Files created by [`Rprof()`](https://www.rdocumentation.org/packages/utils/versions/3.4.3/topics/Rprof)
- `.proto` files written by [`pprof -proto`](https://github.com/google/pprof), these can also be read by `pprof`

The data is available to the user for inspection and manipulation in a [documented stable data format](https://r-prof.github.io/profile/reference/validate_profile.html).

## Installation

You can install profile from GitHub with:

```{r gh-installation, eval = FALSE}
# install.packages("pak")
pak::pak("r-prof/profile")
```

## Example

This simple example converts an `.out` file generated by `Rprof()` to the `.proto` format understood by `pprof`.

```{r example}
rprof_path <- tempfile("profile", fileext = ".out")
Rprof(rprof_path, line.profiling = TRUE)
x <- runif(1e6)
res <- vapply(x, function(x) if (x < 0.5) sqrt(x) else x * x, numeric(1))
Rprof(NULL)

library(profile)
ds <- read_rprof(rprof_path)
ds
names(ds)
write_pprof(ds, file.path(tempdir(), "1.pb.gz"))
```

---

## Code of Conduct

Please note that the profile project is released with a [Contributor Code of Conduct](https://r-prof.github.io/profile/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
