---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# profile

The goal of profile is to read and write files that contain run time profiling data. Currently, profile supports:

- Files created by [`Rprof()`](https://www.rdocumentation.org/packages/utils/versions/3.4.3/topics/Rprof)
- `.proto` files written by [`pprof -proto`](https://github.com/google/pprof), these can also be read by `pprof`

The data is available to the user for inspection and manipulation in a documented stable data format.

## Installation

You can install profile from GitHub with:

```{r gh-installation, eval = FALSE}
# install.packages("remotes")
remotes::install_github("r-prof/profile")
```

## Example

This simple example converts an `.out` file generated by `Rprof()` to the `.proto` format understood by `pprof`.

```{r example}
library(profile)
ds <- read_rprof("tests/testthat/rprof/1.out")
names(ds)
write_pprof(ds, file.path(tempdir(), "1.pb.gz"))
```
